Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-02-16 paper-LIN-PQ.tex
trivial testing

Given a sequence $l$ of priority queue operations, we say that $l$ is data-differentiated, if for each item $d \in \mathcal{D}$, $\textit{put}(d,\_)$ appears at most once in $l$. Note that a data-differentiated sequence $l$ may contains more than one items with a same priority. The subset of data-differentiated operation sequences of a set $S$ is denoted by $S_{\neq}$. For priority queue, the renaming functions rename only the items and keep the priorities unchanged. For priority queue, we modify the notion of data-independence \cite{Wolper:1986} and use data-differentiated instead of differentiated:

>>>>

given a sequence $l$ of priority queue operations, we say that $l$ is data-differentiated, if for each item $d \in \mathcal{D}$, $\textit{put}(d,\_)$ appears at most once in $l$. Note that a data-differentiated sequence $l$ may contains more than one items with a same priority. The subset of data-differentiated operation sequences of a set $S$ is denoted by $S_{\neq}$. For priority queue, the renaming functions rename only the items and keep the priorities unchanged. For priority queue, we modify the notion of data-independence \cite{Wolper:1986} and use data-differentiated instead of differentiated:
